Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-11-15 ms.tex
Some changes in the conductive heating section, as well as in the bib file.

The second source term in equation (\ref{eq:dsdt}) accounts for heating transportation by electron conductivity, where the conductivity $\kappa = \kappa_0 T^{5/2}$ is assumed to equal the classical ``Spitzer" value (\citealt{Spitzer62}); although even a weak magnetic field could in principle strongly suppress the conductivity perpendicular to the field, the radially-decreasing temperature profiles of interest are susceptible to the magneto-thermal instability (\citealt{Balbus01}), the non-linear evolution of which is believed to result in a radially-directed field structure (\citealt{Parrish&Stone07}).

@@

The importance of conductive heating can be estimated by comparing its
magnitude to that of wind heating, viz.~
\begin{eqnarray} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h}\kappa_0
T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
\nonumber \\ &\sim&
0.5\left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
soi}}\right)^{-\beta} v_{500}^{3}\chi^{3},
\end{eqnarray}

where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in the second equality have made use of equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm soi})^{\beta}$ with $\beta \approx 1-2$.  We thus see that conductive heating is important near the stagnation radius for high values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$, but that it is safely neglected to first order for lower heating rates.

@@

\subsection{Comparison with Bondi Accretion}
The spherical accretion rate onto a point source from a surrounding medium of fixed sound speed $c_{\rm s} = (kT/\mu m_p)^{1/2}$ and density is given by (\citealt{Bondi52}) 
\begin{align}
  \dot{M}_{\rm B} =4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b),
\label{eq:bondi}
\end{align}
where $r_b \equiv GM/c_{s}^{2}$ is the ``Bondi radius", $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.

>>>>

The second source term in equation (\ref{eq:dsdt}) accounts for
heating transportation by electron conductivity. We take the
conductivity to be $\kappa_{\rm eff}=\kappa_{\rm spitzer}/(1+\psi)$,
as described in \citealt{DaltonBalbus:1993a}. $\kappa_{\rm spitzer}$
is the classical \citealt{Spitzer62} value, $\kappa_{\rm spitzer} =
\kappa_0 T^{5/2}$ ($\kappa_0\simeq 2\times 10^{-6}$ in cgs units). The
term in the denominator is a flux limiter. The conductive flux should
saturate when the mean free path for electron coulomb scattering
becomes comparable to the temperature length scale.  More precisely
$\psi=\frac{\kappa_{\rm spitzer} \nabla T}{5\phi \rho c_s^3}$ (the
Spitzer conductive flux over the saturated conductive flux; $\phi$ is
a dimensionless constant of order unity or less). Although even a weak
magnetic field could in principle strongly suppress the conductivity
perpendicular to the field, the radially-decreasing temperature
profiles of interest are susceptible to the magneto-thermal
instability (\citealt{Balbus01}), the non-linear evolution of which is
believed to result in a radially-directed field structure
(\citealt{Parrish&Stone07}).

@@

@@

The importance of conductive heating can be estimated by comparing its
magnitude to that of wind heating, viz.~
\begin{eqnarray} \left.\frac{\nabla\cdot(f_{\rm cond})}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim& \frac{2t_{\rm h} \phi \rho(\rs) c_s(\rs)^3}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
\nonumber \\ &\sim&
\frac{10 \phi}{2-\Gamma}, \label{eq:condRatio}
\end{eqnarray}

%Is the stagnation radius the best choice for evaluating the
%importance of conduction? I think it would be greater on the inner
%grid. 
where we have used the saturated heat conduction flux and approximated
$\nabla \sim 1/r_{\rm st}$ and in the second equality have made use of
equations (\ref{eq:Tanalytic}), (\ref{eq:stag_simple}), and
(\ref{eq:rhors}). The stellar density is assumed to be a power law
$\rho_{\star}=\frac{\Mbh \left(2-\Gamma\right)}{4 \pi \rsoi^3}
\left(\frac{\rs}{\rsoi}\right)^{-1-\Gamma}$.
% We thus see that
% conductive heating is important near the stagnation radius for high
% values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$,
% but that it is safely neglected to first order for lower heating
% rates.

By using the saturated value of the conductive heat flux we have found
an upper bound on the ratio of the rate of heating to the rate of heat
conduction is equation~\eqref{eq:condRatio}.  For $\phi\simeq 1$, the
conductive flux could be quite important. However, the value of $\phi$
has some uncertainty as it will depend on various details from plasma
physics, and could plausibly be an order of magnitude smaller. In
light of these uncertainties we neglect the effect of the conductive flux

\begin{align}
  \dot{M}_{\rm B} =4\pi \lambda r_b^2 \rho(r_b) v_{\rm ff}(r_b),
\label{eq:bondi}
\end{align}
where $r_b \equiv GM/c_{s}^{2}$ is the ``Bondi radius", $v_{\rm ff} = (GM_{\bullet}/r)^{1/2}$ and $\lambda$ is a parameter of order unity.
